\mytitle

### 2016-04-26 report/paper.tex
Rewrite some parts

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\def\jocelyn{Jocelyn Thode}
\def\ehsan{Ehsan Farhadi}
\author{\IEEEauthorblockN{\jocelyn\IEEEauthorrefmark{1},
\ehsan\IEEEauthorrefmark{2}}
\IEEEauthorblockA{Université de Neuchâtel\\
Neuchâtel, Switzerland\\
Email: \IEEEauthorrefmark{1}\href{mailto:jocelyn.thode@unifr.ch}{jocelyn.thode@unifr.ch},
\IEEEauthorrefmark{2}\href{mailto:ehsan.farhadi@unine.ch}{ehsan.farhadi@unine.ch}}}

@@

One of the fundamental problems of distributed systems is that a message between two processes, may be delivered zero, or many times. This is way ordering events and messages is an essence in distrusted systems. There has been many algorithm to overcome this problem. EpTO is one of the recently introduced total order algorithms for large-scale distributed systems. EpTO is the first algorithm that claim to provide total order and scalability at the same time. We are going to verify this claim by implementing EpTO and evaluate it in a real-world condition.

@@

The ordering of events is one the most prominent problems in distributed systems \todo[inline]{cite paper}. Creating an algorithm which provides scalability, integrity and validity, along with an ordering for the events through all peers and processes has been one the hot topics in distributed systems research for many years. One of the recently designed algorithms on this topic is EpTO \autocite{matos2015epto}. EpTO is an algorithm which claims to provide integrity, validity and total order in a large scale distributed system. In addition, EpTO is designed to work without a global clock or synchronization process, that is why EpTO is well-suited for dynamic large-scale distributed systems.

@@

explicitly maintain a group and have access to a failure detector \autocites[]{chandra1996weakest}[]{chandra1996unreliable}. Due to the faults and churn in large-scale distributed systems, failure detector turns into bottleneck of the system and thus, limits the scalability of the algorithm.

@@

\section{Ordering Algorithms}
\todo[inline]{We will explain why Ordering algorithms are necessary, the difference between partial order and Total order and why partial order might not be sufficient in some cases}

Distributed systems, like centralized systems need to preserve the temporal order of event produced by concurrent process in the system. When there are separated processes that can only communicate through messages, you can’t easily order these messages.
Therefore we need ordering algorithms to overcome this problem.
\par
We have two types of ordering algorithms \autocite{lamport1978time}: the partial order algorithms and the total order algorithms.
\subsection{Partial Order Algorithms}
Assuming S is partially ordered under $\leq$, then the following statements hold for all a, b and c in S:
\begin{itemize}
	\item Reflexivity: $a \leq a$ for all $a \in S$.
	\item Antisymmetry: $a \leq b$ and $b \leq a$ implies $a=b$ .
	\item Transitivity: $a \leq b$  and $b \leq c$  implies $a \leq c$.
\end{itemize}

\subsection{Total Order Algorithms}
A totally ordered set of events is a partially ordered set which satisfies one additional property:
\begin{itemize}
	\item Totality (trichotomy law): For any $a, b \in S$, either $a \leq b$  or $b \leq a$.
\end{itemize}
\todo[inline]{Explain advantages and usefulness of both systems}
\par
In other words, total order is an ordering that defines the exact order of every event in the system. On the other hand, partial ordering only defines the order between certain key events that depend on each other. Partial order can be useful since it is less costly to implement but, in some cases where the order of all events is important, for example when we need an exact image of the state of the system at all time, we have to use total order.

@@

EpTO is scalable in the sense that \todo[inline]{Explain the logarithmic scalability}

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\def\jocelyn{Jocelyn Thode}
\def\ehsan{Ehsan Farhadi}
\author{
	\IEEEauthorblockN{\jocelyn}
	\IEEEauthorblockA{Université de Fribourg\\
	Fribourg, Switzerland\\
	Email:\href{mailto:jocelyn.thode@unifr.ch}{jocelyn.thode@unifr.ch}
	}
	\and
	\IEEEauthorblockN{\ehsan}
	\IEEEauthorblockA{Université de Neuchâtel\\
		Neuchâtel, Switzerland\\
		Email:\href{mailto:ehsan.farhadi@unine.ch}{ehsan.farhadi@unine.ch}
	}

}

@@

Total ordering has always been of interest in large-scale distributed systems. EpTO is one of the recently introduced total order algorithms for large-scale distributed systems and claims to provide total order and scalability at the same time. In this paper, we verify this claim by implementing EpTO and evaluate its reliability in real-world conditions. We then compare it to a deterministic total order algorithm named JGroups.

@@

Creating an algorithm which provides scalability, integrity and validity, along with a total ordering for the events through all peers in a distributed system has been one the hot topics in distributed systems research for many years. One of the recently designed algorithms on this topic is EpTO \autocite{matos2015epto}. EpTO is an algorithm which claims to provide integrity, validity and total order in a large-scale distributed system. In addition, EpTO is designed to work without a global clock or synchronization process, that is why EpTO is well-suited for dynamic large-scale distributed systems.

@@

explicitly maintain a group and have access to a failure detector \autocites[]{chandra1996weakest}[]{chandra1996unreliable}. Due to faults and churn in large-scale distributed systems, failure detector turns into a bottleneck for the system and thus, limits the scalability of the algorithm.

@@

\section{Ordering Algorithms}
Distributed systems, like centralized systems need to preserve the temporal order of event produced by concurrent process in the system. When there are separated processes that can only communicate through messages, you can’t easily order these messages.
Therefore we need ordering algorithms to overcome this problem.
\par
We have two types of ordering algorithms \autocite{lamport1978time}: the partial order algorithms and the total order algorithms.
\subsection{Partial Order Algorithms}
Assuming S is partially ordered under $\leq$, then the following statements hold for all a, b and c in S:
\begin{itemize}
	\item Reflexivity: $a \leq a$ for all $a \in S$.
	\item Antisymmetry: $a \leq b$ and $b \leq a$ implies $a=b$ .
	\item Transitivity: $a \leq b$  and $b \leq c$  implies $a \leq c$.
\end{itemize}

\subsection{Total Order Algorithms}
A totally ordered set of events is a partially ordered set which satisfies one additional property:
\begin{itemize}
	\item Totality (trichotomy law): For any $a, b \in S$, either $a \leq b$  or $b \leq a$.
\end{itemize}
\par
In other words, total order is an ordering that defines the exact order of every event in the system. On the other hand, partial ordering only defines the order between certain key events that depend on each other. Partial order can be useful since it is less costly to implement. However, in some cases the order of all events is important, for example when we need to know exactly which operations have been invoked in which order, we have to use total order, otherwise we could end up in an inconsistent state.

@@

We define scalable as it was defined in  \autocite{matos2015epto}:  ``The number
of messages transmitted per process per round is logarithmic
in the number of processes, ...''
